### 2008-12-19 talk/ecoop2009/jitgen.tex
add one more para about virtuals, and start the example about promotion
fix an XXX

\cfbolz{XXX: unclear how the next paragraph will fit into the text in the end.
it's certainly wrong as it is}
Once binding times have been determined, one possible approach to
producing the generating extension itself is by self-applying on-line
partial evaluators.  This is known as the second Futamura projection
\cite{Futamura99}.  So far it is unclear if this approach can lead to optimal
results, or even if it scales well.  In PyPy we selected a more direct
approach: the generating extension is produced by transformation of the
control flow graphs of the interpreter, guided by the binding times.  We
call this process \emph{timeshifting}.

@@

XXX need better transition text from last section
At translation time, PyPy performs binding-time analysis of the source
RPython program after it has been turned to low-level graphs, i.e. at
the level at which operations manipulate pointer-and-structure-like
objects.

@@

The binding-time analyzer of our translation tool-chain is using a simple
abstract-interpretation based analysis. It is based on the
same type inference engine that is used on the source RPython program,
the annotator \anto{I'm not sure we should mention the annotator, as it is not referred anywhere else}.  In this mode, it is called the \emph{hint-annotator}; it
operates over input graphs that are already low-level instead of
RPython-level, and propagates annotations that do not track types but
value dependencies and manually-provided binding time hints.
XXX the above needs rewriting when the background section is there

@@

XXX move this to the promotion section
Promotion is invoked with the use of a hint as well:
\texttt{v2 = hint(v1, promote=True)}.
This hint is a \emph{local} request for \texttt{v2} to be green, without
requiring \texttt{v1} to be green.  Note that this amounts to copying
a red value into a green one, which is not possible in classical
approaches to partial evaluation.  See Section \ref{sec:promotion} for a
complete discussion of promotion.

>>>>

@@

XXX need better transition text from last section
At translation time, PyPy performs binding-time analysis of the source
RPython program after it has been turned to low-level graphs, i.e. at
the level at which operations manipulate objects that have a fixed type
attached.

@@

The binding-time analyzer of our translation tool-chain is using a simple
abstract-interpretation based analysis. It is based on the
same type inference engine that is used on the source RPython program.
This is called the \emph{hint-annotator}; it
operates over input graphs that are already low-level instead of
RPython-level, and propagates annotations that do not track types but
value dependencies and manually-provided binding time hints.

@@

### 2008-12-19 talk/ecoop2009/rainbow.tex
fix an XXX

>>>>

Promotion is invoked with the use of a hint as well:
\texttt{v2 = hint(v1, promote=True)}.
This hint is a \emph{local} request for \texttt{v2} to be green, without
requiring \texttt{v1} to be green.  Note that this amounts to copying
a red value into a green one, which is not possible in classical
approaches to partial evaluation. A slightly different hint can be used to
promote the \emph{class} of an instance. This is done with \lstinline{hint(v1,
promote_class=True)}. It does not have an effect on the bindings of any
variable.
